Contextuality and Nonlocality in Discrete Quantum Theory

### 2015-11-25 DQC3.tex
Adding more comments on "The Concept of Contextuality and its..."

\yutsung{Does the sentences in this paragraph contradict to each
other? I think Peres~\cite{peres1995quantum} means: If we think
the measurement process as a quantum system by the Born rule, the
measurement result does not depend on simultaneously measuring commuting
observables. On the other hand, if we want to think the measurement
process classically, i.e., to assign the measurement result for each
observable, we cannot make the assignment prior to any measurement,
and assume that measuring commuting observables does not change the
assigned measurement result. <- This long sentence means contextuality.}

>>>>

\yutsung{Does the sentences in this paragraph contradict to each
other? Besides, are we talking about CQT or DQT here? The paragraph
make sense because we can simultaneously measuring commuting observables
in CQT. However, if $J_{z}$ and $J_{z}^{2}$ cannot measure simultaneously,
then I doubt whether any observables can measure simultaneously. Furthermore,
the definition of contextuality is based on simultaneously measurement
in CQT so that we must be very careful to re-define the contextuality
in DQT to bypass the simultaneously measurement...

I think Peres~\cite{peres1995quantum} means: If we think the measurement
process as a quantum system by the Born rule, the measurement result
does not depend on simultaneously measuring commuting observables.
On the other hand, if we want to think the measurement process classically,
i.e., to assign the measurement result for each observable, we cannot
make the assignment prior to any measurement, and assume that measuring
commuting observables does not change the assigned measurement result.
<- This long sentence means contextuality.}
